The Proofs

### 2024-07-31 proofs/tex/alg-pos-subtyping-lemmas.tex
prettify + minor edits

    \item \label{case:pos-subt-soundness:shift} 
        \ruleref{\ottdruleAShiftDLabel} then
        $[[Γ ; Θ ⊨ uP ≥ iQ ⫤ SC]]$ has shape $[[Γ;Θ ⊨ ↓uN ≥ ↓iM ⫤ SC]]$.\\
        Then the next step of the algorithm is the unification of $[[nf(uN)]]$ and $[[nf(iM)]]$,
        and it returns the resulting unification constraint $[[lift UC]] = [[SC]]$ as the result.
        By the soundness of unification (\cref{lemma:unification-soundness}),
        $[[Θ ⊢ SC : uv(uN)]]$ and for any normalized $[[uσ]]$, $[[ Θ ⊢ uσ : SC ]]$
        implies $[[ [uσ]nf(uN) = nf(iM) ]]$, 
        then we rewrite the left-hand side by \cref{lemma:norm-subst-distr}:
        $[[ nf([uσ]uN) = nf(iM) ]]$ and apply \cref{lemma:subt-equiv-algorithmization}:
        $[[Γ ⊢ [uσ]uN ≈ iM]]$, then by \ruleref{\ottdruleDOneShiftULabel},
        $[[Γ ⊢ ↓[uσ]uN ≥ ↓iM]]$.

@@

            \begin{itemize}
                \item $[[nf(uN)]]$ and $[[nf(iM)]]$ are normalized 
                \item $[[Γ ; dom(Θ) ⊢  nf(uN)]]$ because $[[Γ ; dom(Θ) ⊢  uN]]$ (\cref{corollary:wf-nf-algo})
                \item $[[Γ ⊢ nf(iM)]]$ because $[[Γ ⊢ iM]]$ (\cref{corollary:wf-nf})
                \item $[[ Θ ⊢ nf(uσ) : uv(uP) ]]$ because $[[Θ ⊢ uσ : uv(uP) ]]$ (\cref{corollary:norm-subst-sig-algo})
                \item \begin{align*}
                        [[ Γ ⊢ [uσ]uN ≈ iM ]] &\Rightarrow [[ [uσ]uN ≈ iM ]]
                                            && \text {by \cref{lemma:equiv-completeness}}\\
                                            &\Rightarrow [[ nf([uσ]uN) = nf(iM) ]]
                                            && \text {by \cref{lemma:normalization-completeness}}\\
                                            &\Rightarrow [[ [nf(uσ)]nf(uN) = nf(iM) ]]
                                            && \text {by \cref{lemma:norm-subst-distr}}\\
                        \end{align*}
            \end{itemize}
            By the completeness of the unification,
            $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$ exists, and
            $[[Θ ⊢ nf(uσ) : lift UC]]$,
            and by \cref{corollary:sat-equiv}, $[[ Θ ⊢ uσ : lift UC ]]$.

@@

            To show that the recursive call terminates and that 
            $[[ Θ ⊢ uσ : SC1 \ {â⁻*} ]]$,
            it suffices to build $[[Θ, â⁻*[G, nbs] ⊢ us0 : uv(uP0)]]$---an extension of $[[uσ]]$ with
            $[[{â⁻*} ∩ uv(uP0)]]$ such that $[[Γ, nbs ⊢ [us0]uP0 ≥ iQ]]$.
            Then by the induction hypothesis, $[[Θ, â⁻*[G, nbs] ⊢ us0 : SC1]]$,
            and hence, $[[ Θ  ⊢ uσ : SC1 \ {â⁻*} ]]$, as required.

            Let us construct such a substitution $[[us0]]$:
                \[
                    [[ [uσ0]β̂± ]]  = 
                    \begin{cases}
                    [[ [σ]αi⁻ ]] & \text{if } [[β̂±]] = [[αî⁻]] \in [[{â⁻*} ∩ uv(uP0)]] \\
                    [[ [uσ]β̂± ]] & \text{if } [[β̂±]] \in [[ uv(uP') ]]
                    \end{cases}
            \]
            It is easy to see $[[Θ, â⁻*[Γ, nbs] ⊢ uσ0 : uv(uP0)]]$:
            $[[uv(uP0)]] = [[ uv([â⁻*/nas]uP') ]] = [[{â⁻*} ∩ uv(uP0) ∪ uv(uP')]]$. Then
            \begin{enumerate}
                    \item for $[[αî⁻]] \in [[{â⁻*} ∩ uv(uP0)]]$, $[[ (Θ, â⁻*[Γ, nbs])(αî⁻) ⊢ [uσ0] αî⁻]]$, 
                    i.e. $[[ Γ, nbs ⊢ [σ]αi⁻ ]]$ holds since $[[Γ, nbs ⊢ σ :{nas}]]$,
                    \item for $[[β̂±]] \in [[ uv(uP') ]] \subseteq [[dom(Θ)]]$, $[[ (Θ, â⁻*[Γ, nbs])(β̂±) ⊢ [uσ0] β̂± ]]$,
                    i.e. $[[Θ(β̂±) ⊢ [uσ] β̂± ]]$ holds since $[[Θ ⊢ uσ : uv(uP)]]$ and $[[β̂±]] \in [[ uv(uP') ]] = [[uv(uP)]]$.
            \end{enumerate}

            Now, let us show that $[[Γ, nbs ⊢ [us0]uP0 ≥ iQ]]$.
            To do that, we notice that\\ $[[ [uσ0]uP0 ]] = [[ [uσ][σ][nas/â⁻*]uP0 ]]$:
            let us consider an arbitrary variable appearing freely in $[[uP0]]$:
            \begin{enumerate}
                \item if this variable is a algorithmic variable $[[αî⁻]] \in [[â⁻*]]$, then
                $[[ [uσ0]αî⁻ ]] = [[ [σ]αi⁻ ]]$ and\\
                $[[ [uσ][σ][nas/â⁻*]αî⁻ ]] = [[ [uσ][σ]αi⁻ ]] = [[ [σ]αi⁻ ]]$,
                \item if this variable is a algorithmic variable $[[β̂±]] \in [[ uv(uP0) \ {â⁻*} ]] = [[uv(uP')]]$, then
                $[[ [uσ0]β̂± ]] = [[ [uσ]β̂± ]]$ and $[[ [uσ][σ][nas/â⁻*]β̂± ]] = [[ [uσ][σ]β̂± ]] = [[ [uσ]β̂± ]]$,
                \item if this variable is a regular variable from $[[fv(uP0)]]$, both substitutions do not change it:
                $[[ uσ0 ]]$, $[[ uσ ]]$ and $[[ nas / â⁻* ]]$ act on algorithmic variables, 
                and $[[σ]]$ is defined on $[[nas]]$, however, $[[{nas} ∩ fv(uP0) = ∅]]$.
            \end{enumerate}
            This way, $[[ [uσ0]uP0 ]] = [[ [uσ][σ][nas/â⁻*]uP0 ]] = [[ [uσ][σ]uP' ]]$,
            and thus, $[[ Γ, nbs ⊢ [uσ0]uP0 ≥ iQ' ]]$.
    \end{caseof}
\end{proof}

>>>>

    \item \label{case:pos-subt-soundness:shift} 
        \ruleref{\ottdruleAShiftDLabel} then
        $[[Γ ; Θ ⊨ uP ≥ iQ ⫤ SC]]$ has shape $[[Γ;Θ ⊨ ↓uN ≥ ↓iM ⫤ SC]]$.\\
        Then the next step of the algorithm is the unification of $[[nf(uN)]]$ and $[[nf(iM)]]$,
        and it returns the resulting unification constraint $[[lift UC]] = [[SC]]$ as the result.
        By the soundness of unification (\cref{lemma:unification-soundness}),
        $[[Θ ⊢ SC : uv uN]]$ and for any normalized $[[uσ]]$, $[[ Θ ⊢ uσ : SC ]]$
        implies $[[ [uσ]nf(uN) = nf(iM) ]]$, 
        then we rewrite the left-hand side by \cref{lemma:norm-subst-distr}:
        $[[ nf([uσ]uN) = nf(iM) ]]$ and apply \cref{lemma:subt-equiv-algorithmization}:
        $[[Γ ⊢ [uσ]uN ≈ iM]]$, then by \ruleref{\ottdruleDOneShiftULabel},
        $[[Γ ⊢ ↓[uσ]uN ≥ ↓iM]]$.

@@

            \begin{itemize}
                \item $[[nf(uN)]]$ and $[[nf(iM)]]$ are normalized 
                \item $[[Γ ; dom(Θ) ⊢  nf(uN)]]$ because $[[Γ ; dom(Θ) ⊢  uN]]$ (\cref{corollary:wf-nf-algo})
                \item $[[Γ ⊢ nf(iM)]]$ because $[[Γ ⊢ iM]]$ (\cref{corollary:wf-nf})
                \item $[[ Θ ⊢ nf(uσ) : uv uP ]]$ because $[[Θ ⊢ uσ : uv uP ]]$ (\cref{corollary:norm-subst-sig-algo})
                \item \begin{align*}
                        [[ Γ ⊢ [uσ]uN ≈ iM ]] &\Rightarrow [[ [uσ]uN ≈ iM ]]
                                            && \text {by \cref{lemma:equiv-completeness}}\\
                                            &\Rightarrow [[ nf([uσ]uN) = nf(iM) ]]
                                            && \text {by \cref{lemma:normalization-completeness}}\\
                                            &\Rightarrow [[ [nf(uσ)]nf(uN) = nf(iM) ]]
                                            && \text {by \cref{lemma:norm-subst-distr}}\\
                        \end{align*}
            \end{itemize}
            By the completeness of the unification,
            $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$ exists, and
            $[[Θ ⊢ nf(uσ) : lift UC]]$,
            and by \cref{corollary:sat-equiv}, $[[ Θ ⊢ uσ : lift UC ]]$.

@@

            To show that the recursive call terminates and that 
            $[[ Θ ⊢ uσ : SC1 \ {â⁻*} ]]$,
            it suffices to build $[[Θ, â⁻*[G, nbs] ⊢ us0 : uv uP0]]$---an extension of $[[uσ]]$ with
            $[[{â⁻*} ∩ uv uP0]]$ such that $[[Γ, nbs ⊢ [us0]uP0 ≥ iQ]]$.
            Then by the induction hypothesis, $[[Θ, â⁻*[G, nbs] ⊢ us0 : SC1]]$,
            and hence, $[[ Θ  ⊢ uσ : SC1 \ {â⁻*} ]]$, as required.

            Let us construct such a substitution $[[us0]]$:
                \[
                    [[ [uσ0]β̂± ]]  = 
                    \begin{cases}
                    [[ [σ]αi⁻ ]] & \text{if } [[β̂±]] = [[αî⁻]] \in [[{â⁻*} ∩ uv uP0]] \\
                    [[ [uσ]β̂± ]] & \text{if } [[β̂±]] \in [[ uv uP' ]]
                    \end{cases}
            \]
            It is easy to see $[[Θ, â⁻*[Γ, nbs] ⊢ uσ0 : uv uP0]]$:
            $[[uv uP0]] = [[ uv [â⁻*/nas]uP' ]] = [[{â⁻*} ∩ uv uP0 ∪ uv uP']]$. Then
            \begin{enumerate}
                    \item for $[[αî⁻]] \in [[{â⁻*} ∩ uv uP0]]$, $[[ (Θ, â⁻*[Γ, nbs])(αî⁻) ⊢ [uσ0] αî⁻]]$, 
                    i.e. $[[ Γ, nbs ⊢ [σ]αi⁻ ]]$ holds since $[[Γ, nbs ⊢ σ :{nas}]]$,
                    \item for $[[β̂±]] \in [[ uv uP' ]] \subseteq [[dom(Θ)]]$, $[[ (Θ, â⁻*[Γ, nbs])(β̂±) ⊢ [uσ0] β̂± ]]$,
                    i.e. $[[Θ(β̂±) ⊢ [uσ] β̂± ]]$ holds since $[[Θ ⊢ uσ : uv uP]]$ and $[[β̂±]] \in [[ uv uP' ]] = [[uv uP]]$.
            \end{enumerate}

            Now, let us show that $[[Γ, nbs ⊢ [us0]uP0 ≥ iQ]]$.
            To do that, we notice that\\ $[[ [uσ0]uP0 ]] = [[ [uσ][σ][nas/â⁻*]uP0 ]]$:
            let us consider an arbitrary variable appearing freely in $[[uP0]]$:
            \begin{enumerate}
                \item if this variable is a algorithmic variable $[[αî⁻]] \in [[â⁻*]]$, then
                $[[ [uσ0]αî⁻ ]] = [[ [σ]αi⁻ ]]$ and\\
                $[[ [uσ][σ][nas/â⁻*]αî⁻ ]] = [[ [uσ][σ]αi⁻ ]] = [[ [σ]αi⁻ ]]$,
                \item if this variable is a algorithmic variable $[[β̂±]] \in [[ uv uP0 \ {â⁻*} ]] = [[uv uP']]$, then
                $[[ [uσ0]β̂± ]] = [[ [uσ]β̂± ]]$ and $[[ [uσ][σ][nas/â⁻*]β̂± ]] = [[ [uσ][σ]β̂± ]] = [[ [uσ]β̂± ]]$,
                \item if this variable is a regular variable from $[[fv(uP0)]]$, both substitutions do not change it:
                $[[ uσ0 ]]$, $[[ uσ ]]$ and $[[ nas / â⁻* ]]$ act on algorithmic variables, 
                and $[[σ]]$ is defined on $[[nas]]$, however, $[[{nas} ∩ fv(uP0) = ∅]]$.
            \end{enumerate}
            This way, $[[ [uσ0]uP0 ]] = [[ [uσ][σ][nas/â⁻*]uP0 ]] = [[ [uσ][σ]uP' ]]$,
            and thus, $[[ Γ, nbs ⊢ [uσ0]uP0 ≥ iQ' ]]$.
    \end{caseof}
\end{proof}

### 2024-07-31 proofs/tex/constraint-merge-lemmas.tex
prettify + minor edits

            Let us show the required properties.
            \begin{itemize}
                \item By assumption, $[[Γ ⊢ iQ]]$, and hence $[[Γ ⊢ scE]]$.
                \item Since $[[uv(uQ2) = ∅]]$, 
                    $[[Γ;· ⊨ uQ2 ≥ iQ1 ⫤ ·]]$ implies $[[Γ ⊢ iQ2 ≥ iQ1]]$
                    by the soundness of positive subtyping (\cref{lemma:pos-subt-soundness}).
                    Then let us take an arbitrary $[[Γ ⊢ iP]]$ such that $[[Γ ⊢ iP : scE]]$.
                    Since $[[scE2]] = [[scE]]$, $[[Γ ⊢ iP : scE2]]$ holds immediately.

>>>>

            Let us show the required properties.
            \begin{itemize}
                \item By assumption, $[[Γ ⊢ iQ]]$, and hence $[[Γ ⊢ scE]]$.
                \item Since $[[uv uQ2 = ∅]]$, 
                    $[[Γ;· ⊨ uQ2 ≥ iQ1 ⫤ ·]]$ implies $[[Γ ⊢ iQ2 ≥ iQ1]]$
                    by the soundness of positive subtyping (\cref{lemma:pos-subt-soundness}).
                    Then let us take an arbitrary $[[Γ ⊢ iP]]$ such that $[[Γ ⊢ iP : scE]]$.
                    Since $[[scE2]] = [[scE]]$, $[[Γ ⊢ iP : scE2]]$ holds immediately.

### 2024-07-31 proofs/tex/norm-lemmas.tex
prettify + minor edits

      $[[ [nf(σ)] nf(iN) ]] = [[ [nf(σ)] nf(na) ]] = [[ [nf(σ)] na ]] $.
    \item $[[iP]]$ = $[[pa]]$ \\
      Similar to \cref{case:norm-subst-distr-var}.
   \item If the type is formed by $[[→]]$, $[[↑]]$, or $[[↓]]$, 
     the required equality follows from the congruence of the normalization and
     substitution and the induction hypothesis.
     For example, if $[[iN]] = [[iP → iM]]$ then
     \begin{align*}
        [[nf([σ] iN)]] &= [[ nf([σ] (iP → iM)) ]] \\
                        &= [[ nf([σ]iP → [σ]iM) ]]
                        && \text{By congruence of substitution} \\
                        &= [[ nf([σ]iP) → nf([σ]iM) ]]
                        && \text{By congruence of normalization} \\
                        &= [[ [nf(σ)]nf(iP) → [nf(σ)]nf(iM) ]]
                        && \text{By induction hypothesis} \\
                        &= [[ [nf(σ)](nf(iP) → nf(iM)) ]]
                        && \text{By congruence of substitution} \\
                        &= [[ [nf(σ)]nf(iP → iM) ]]
                        && \text{By congruence of normalization} \\
                        &= [[ [nf(σ)]nf(iN) ]]
      \end{align*}
    \item $[[iN]] = [[∀ pas.iM]]$ \label{case:norm-subst-commute}
      \begin{align*}
          [[ [nf(σ)] nf(iN) ]] &= [[ [nf(σ)] nf(∀pas.iM)]] \\
                            &= [[ [nf(σ)] ∀pas'.nf(iM) ]]
                            && \text {Where $[[pas']] = [[ ord {pas} in nf(iM)]]
                               = [[ord {pas} in iM]]$}\\
                           & && 
                               \text{(the latter is by
                               \cref{corollary:normalization-ord})}\\
        \end{align*}

      \begin{align*}
         [[ nf([σ]iN) ]] &= [[ nf([σ] ∀pas.iM)]] \\
                          &= [[ nf(∀pas.[σ]iM) ]]
                          && \text{Assuming $[[{pas} ∩ Γ1]] = \emptyset$
                             and $[[{pas} ∩ Γ2]] = \emptyset$}\\
                          &= [[ ∀pbs.nf([σ]iM) ]]
                          && \text {Where $[[pbs]] = [[ord {pas} in nf([σ]iM)]]
                             = [[ord {pas} in [σ]iM]]$}\\
                          & && 
                             \text{(the latter is by \cref{corollary:normalization-ord})}\\
                          &= [[ ∀pas'.nf([σ]iM) ]]
                          && \text{By \cref{lemma:ord-sigma},}\\
                          & && \text{$[[pbs]] = [[pas']]$
                             since $[[{pas}]]$ is disjoint with $[[Γ1]]$ and
                             $[[Γ2]]$}\\
                          &= [[ ∀pas'.[nf(σ)]nf(iM) ]]
                          && \text {By the induction hypothesis}\\
         \end{align*}
     To show the alpha-equivalence of 
     $[[ [nf(σ)] ∀pas'.nf(iM) ]]$ and $[[ ∀pas'.[nf(σ)]nf(iM) ]]$,
     we can assume that $[[{pas'} ∩ Γ1]] = \emptyset$, and $[[{pas'} ∩ Γ2]]
     = \emptyset$.

@@

    \item[(ii)] 
    \begin{align*} 
      [[ [mu]pbs' ]] &= [[ [mu] ord {pbs} in nf(iM) ]]
                      && \text{by the definition of $[[pbs']]$ } \\
                      &= [[ [mu] ord ({pbs} ∩ fv iM) in nf(iM) ]]
                      && \text{from \cref{lemma:fv-nf,corollary:ord-weakening} } \\
                      &= [[ ord [mu] ({pbs} ∩ fv iM) in [mu] nf(iM) ]]
                      && \text{by \cref{lemma:distr-mu-ord}, because}\\
                      & && \text{$[[{pas} ∩ fv iN]] \cap [[fv nf(iM)]] \subseteq [[{pas} ∩ fv iM ]]
                        = \emptyset$}\\
                      &
                      && \text{$[[{pas} ∩ fv iN]] \cap [[({pbs} ∩ fv iM)]] \subseteq
                        [[{pas} ∩ fv iM]] = \emptyset$} \\
                      &= [[ ord [mu] ({pbs} ∩ fv iM) in nf(iN) ]]
                      && \text{since $[[ [mu] nf(iM) ]] = [[nf(iN)]]$ is proved } \\
                      &= [[ ord ({pas} ∩ fv iN) in nf(iN) ]]
                      && \text{because $\mu$ is a bijection between}\\
                      & && \text{$[[{pas} ∩ fv iN]]$ and $[[{pbs} ∩ fv iM]]$} \\
                      &= [[ ord {pas} in nf(iN) ]]
                      && \text{from \cref{lemma:fv-nf,corollary:ord-weakening} } \\
                      &= [[ pas' ]]
                      && \text{by the definition of $[[pas']]$} \\
      \end{align*}
    \end{enumerate}
  \item {\nameref{\ottdruleEOneExistsLabel}} Same as for \cref{case:ord-completeness:forall}.
  \item Other rules are congruent, and thus, proved by the corresponding congruent alpha-equivalence rule,
    which is applicable by the induction hypothesis. 
  \end{caseof}
\end{proof}

@@

                                           && \text{by substitution
                                              congruence} \\

@@

>>>>

      $[[ [nf(σ)] nf(iN) ]] = [[ [nf(σ)] nf(na) ]] = [[ [nf(σ)] na ]] $.
    \item $[[iP]]$ = $[[pa]]$ \\
      Similar to \cref{case:norm-subst-distr-var}.
   \item If the type is formed by $[[→]]$, $[[↑]]$, or $[[↓]]$, 
     the required equality follows from the congruence of the normalization and
     substitution and the induction hypothesis.
     For example, if $[[iN]] = [[iP → iM]]$ then
     \begin{align*}
        [[nf([σ] iN)]] &= [[ nf([σ] (iP → iM)) ]] \\
                        &= [[ nf([σ]iP → [σ]iM) ]]
                        && \text{by congruence of substitution} \\
                        &= [[ nf([σ]iP) → nf([σ]iM) ]]
                        && \text{by congruence of normalization} \\
                        &= [[ [nf(σ)]nf(iP) → [nf(σ)]nf(iM) ]]
                        && \text{by induction hypothesis} \\
                        &= [[ [nf(σ)](nf(iP) → nf(iM)) ]]
                        && \text{by congruence of substitution} \\
                        &= [[ [nf(σ)]nf(iP → iM) ]]
                        && \text{by congruence of normalization} \\
                        &= [[ [nf(σ)]nf(iN) ]]
      \end{align*}
    \item $[[iN]] = [[∀ pas.iM]]$ \label{case:norm-subst-commute}
      \begin{align*}
          [[ [nf(σ)] nf(iN) ]] &= [[ [nf(σ)] nf(∀pas.iM)]] \\
                            &= [[ [nf(σ)] ∀pas'.nf(iM) ]]
                            && \text {where $[[pas']] = [[ ord {pas} in nf(iM)]]$}\\
                            & && = [[ord {pas} in iM]]\\
                            & && \text{(the latter is by \cref{corollary:normalization-ord})}\\
        \end{align*}

      \begin{align*}
         [[ nf([σ]iN) ]] &= [[ nf([σ] ∀pas.iM)]] \\
                          &= [[ nf(∀pas.[σ]iM) ]]
                          && \text{assuming $[[{pas} ∩ Γ1]] = \emptyset$
                             and $[[{pas} ∩ Γ2]] = \emptyset$}\\
                          &= [[ ∀pbs.nf([σ]iM) ]]
                          && \text {where $[[pbs]] = [[ord {pas} in nf([σ]iM)]]$}\\
                          & && = [[ord {pas} in [σ]iM]]\\
                          & && \text{(the latter is by \cref{corollary:normalization-ord})}\\
                          &= [[ ∀pas'.nf([σ]iM) ]]
                          && \text{by \cref{lemma:ord-sigma},}\\
                          & && \text{$[[pbs]] = [[pas']]$
                             since $[[{pas}]]$ is disjoint with $[[Γ1]]$ and
                             $[[Γ2]]$}\\
                          &= [[ ∀pas'.[nf(σ)]nf(iM) ]]
                          && \text {by the induction hypothesis}\\
         \end{align*}
     To show the alpha-equivalence of 
     $[[ [nf(σ)] ∀pas'.nf(iM) ]]$ and $[[ ∀pas'.[nf(σ)]nf(iM) ]]$,
     we can assume that $[[{pas'} ∩ Γ1]] = \emptyset$, and $[[{pas'} ∩ Γ2]]
     = \emptyset$.

@@

    \item[(ii)] 
    \begin{align*} 
      [[ [mu]pbs' ]] &= [[ [mu] ord {pbs} in nf(iM) ]]
                      && \text{by the definition of $[[pbs']]$ } \\
                      &= [[ [mu] ord ({pbs} ∩ fv iM) in nf(iM) ]]
                      && \text{from \cref{lemma:fv-nf,corollary:ord-weakening} } \\
                      &= [[ ord [mu] ({pbs} ∩ fv iM) in [mu] nf(iM) ]]
                      && \text{by \cref{lemma:distr-mu-ord}, because}\\
      &  \omit\rlap{\hspace{5em} $[[{pas} ∩ fv iN]] \cap [[fv nf(iM)]] \subseteq [[{pas} ∩ fv iM ]] = \emptyset$, and}\\ 
      &  \omit\rlap{\hspace{5em} $[[{pas} ∩ fv iN]] \cap [[({pbs} ∩ fv iM)]] \subseteq [[{pas} ∩ fv iM]] = \emptyset$}\\ 
                      &= [[ ord [mu] ({pbs} ∩ fv iM) in nf(iN) ]]
                      && \text{as $[[ [mu] nf(iM) ]] = [[nf(iN)]]$} \\
                      &= [[ ord ({pas} ∩ fv iN) in nf(iN) ]]
                      && \text{$\mu$ is a bijection between}\\
                      & && \text{$[[{pas} ∩ fv iN]]$ and $[[{pbs} ∩ fv iM]]$} \\
                      &= [[ ord {pas} in nf(iN) ]]
                      && \text{from \cref{lemma:fv-nf,corollary:ord-weakening} } \\
                      &= [[ pas' ]]
                      && \text{by the definition of $[[pas']]$} \\
      \end{align*}
    \end{enumerate}
  \item {\nameref{\ottdruleEOneExistsLabel}} Same as for \cref{case:ord-completeness:forall}.
  \item Other rules are congruent, and thus, proved by the corresponding congruent alpha-equivalence rule,
    which is applicable by the induction hypothesis. 
  \end{caseof}
\end{proof}

@@

                                           && \text{substitution definition} \\

@@

                                           && \text{induction hypothesis}\\
